SETI in the Spatial-Temporal Domain

### 2016-09-19 paper/ms.tex
change paper style

%\documentclass[]{openjournal}
\documentclass[iop]{emulateapj}

\bibliographystyle{apj}
\usepackage{graphicx}
\usepackage[suffix=]{epstopdf}
\usepackage[export]{adjustbox}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{url}
\usepackage{xspace}

@@

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%
\title{SETI in the Spatial-Temporal Domain: Spatially Coordinated Transits as an ET Signal}

\shorttitle{SETI in the Spatial-Temporal Domain}
\shortauthors{Davenport et al.}

\author{
	James R. A. Davenport\altaffilmark{1,2,3}
	}

\altaffiltext{1}{Corresponding author: James.Davenport@wwu.edu}
\altaffiltext{2}{Department of Physics \& Astronomy, Western Washington University, Bellingham, WA 98225}
\altaffiltext{3}{NSF Astronomy and Astrophysics Postdoctoral Fellow}

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coordinated Transits as ET Beacons}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Predictions for Upcoming Surveys}
TESS would be great for this in terms of spatial-temporal coverage.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}

>>>>

%\documentclass[]{openjournal}
\documentclass[manuscript, letterpaper]{aastex6}
\bibliographystyle{aasjournal}

\bibliographystyle{apj}
\usepackage{graphicx}
\usepackage[suffix=]{epstopdf}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{url}
\usepackage{xspace}

% from here: https://github.com/dfm/peerless/blob/master/document/ms.tex#L19-L69
% ----------------------------------- %
% start of AASTeX mods by DWH and DFM %
% ----------------------------------- %

\setlength{\voffset}{0in}
\setlength{\hoffset}{0in}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setlength{\headheight}{0ex}
\setlength{\headsep}{\baselinestretch\baselineskip} % this is 2 lines in ``manuscript''
\setlength{\footnotesep}{0in}
\setlength{\topmargin}{-\headsep}
\setlength{\oddsidemargin}{0.25in}
\setlength{\evensidemargin}{0.25in}

\linespread{0.54} % close to 10/13 spacing in ``manuscript''
\setlength{\parindent}{0.54\baselineskip}
\hypersetup{colorlinks = false}
\makeatletter % you know you are living your life wrong when you need to do this
\long\def\frontmatter@title@above{
\vspace*{-\headsep}\vspace*{\headheight}
\noindent\footnotesize
{\noindent\footnotesize\textsc{\@journalinfo}}\par
{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6\\
With modifications by David W. Hogg and Daniel Foreman-Mackey
}\par\vspace*{-\baselineskip}\vspace*{0.625in}
}%
\makeatother

% Section spacing:
\makeatletter
\let\origsection\section
\renewcommand\section{\@ifstar{\starsection}{\nostarsection}}
\newcommand\nostarsection[1]{\sectionprelude\origsection{#1}}
\newcommand\starsection[1]{\sectionprelude\origsection*{#1}}
\newcommand\sectionprelude{\vspace{1em}}
\let\origsubsection\subsection
\renewcommand\subsection{\@ifstar{\starsubsection}{\nostarsubsection}}
\newcommand\nostarsubsection[1]{\subsectionprelude\origsubsection{#1}}
\newcommand\starsubsection[1]{\subsectionprelude\origsubsection*{#1}}
\newcommand\subsectionprelude{\vspace{1em}}
\makeatother

\widowpenalty=10000
\clubpenalty=10000

\sloppy\sloppypar

% ------------------ %
% end of AASTeX mods %
% ------------------ %

@@

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%
\title{SETI in the Spatial-Temporal Domain}

\shorttitle{SETI in the Spatial-Temporal Domain}
\shortauthors{Davenport}

\author{
	James R. A. Davenport\altaffilmark{1,2}
	}

%\altaffiltext{1}{Corresponding author: James.Davenport@wwu.edu}
\altaffiltext{1}{Department of Physics \& Astronomy, Western Washington University, Bellingham, WA 98225}
\altaffiltext{2}{NSF Astronomy and Astrophysics Postdoctoral Fellow}

@@

optical seti
http://arxiv.org/abs/astro-ph/0506758

@@

active and passive SETI in coordination (both temporal and spatial) with galactic events like supernovae 
\citep{lemarchand1994}

lighthouses
\citep{zuluaga2015}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Example: Coordinated Transits as ET Beacons}
imagine a Type N civilization with the ability to both travel to nearby star systems, and to build large enough structures in orbit around other stars to produce a visible transit in our data.

give the detailed example i have thought up.

becons placed at distances

@@

for clarity, this is what the ideal signal might look like on the sky

@@

%and then what it might look like in 3d, projected in to 2d

%%%

this type of beacon network is advantageous because it points directly back towards their home. only a few systems actually need to be transiting from any given line of sight.

NOW THE FULL SIMULATION...
- computation to do: if had 100 beacons, each placed at random orbital alignment, in 3d sphere around home system.
- assume G stars, 
- odds of observing transit of a fixed sized object versus orbital distance... goes down. need that plot to figure out probability. 
- assume ET places beacons with uniform RADIAL density in 3d space out to some maximum distance (even \# of systems as function of radial distance) in bins of 10pc out to 100 pc (i.e. 10 beacons in each 10pc bin)
- orbital period is exact for each system, no bins of period
- do Monte Carlo sim with these parameters to figure out how many transiting systems we'd observe

---- make the plot for one MC realization of RA,Dec.... open circles for systems with no observed transits, colored for transits

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Prospects for Future Surveys}

to get accurate census you need a complete time domain survey at some transit depth sensitivity out to some orbital period. going off our simulation, TESS might work for very short period planets

TESS would be great for this in terms of spatial-temporal coverage.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
this kind of distributed network could be very efficient at broadcasting the presence of a civilization. dust clouds could create sufficient "transit" signals, while not affecting orbital dynamics
